Is Crime Really On A Rise In Toronto? An Analysis of The Past And Current Crime Rates of Toronto

### 2024-01-19 outputs/paper/paper.qmd
updated paper

The data utilized throughout this paper was obtained through the City of Toronto's

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

@@

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

final_percentage_change_table |> kable()
```

@@

percentage_change_table |> kable()
```

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

>>>>

The data utilized throughout this paper was obtained through the City of Toronto's OpenDataToronto [@citeOpenDataToronto]. The specific data set that was used is entitled 'Neighbourhood Crime Rates, 2023' [@citeData]. Data was collected and analyzed through the statistical program 'R' [@citeR]

@@

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of . We use the default priors from `rstanarm`.

@@

colnames(final_percentage_change_table) <- c("X", "Crime", "Percentage Change")

final_percentage_change_table |> select("Crime", "Percentage Change") |> kable()
```

@@

colnames(percentage_change_table) <- c("X", "Crime", "Percentage Change")
percentage_change_table |> select("Crime", "Percentage Change") |> kable()
```

@@

In we implement a posterior predictive check. This shows...

In we compare the posterior with the prior. This shows...
